---
title: "Project Proposal"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      error = TRUE, 
                      warning = FALSE, 
                      message = FALSE)
library(tidyverse)
```


# Section 316:2 

### Holly Brikowski, Claire Chen, Anthony Thomas, Garrett Wink

> When during the week can the group meet? Consider needs of all group members.

- We plan to meet Monday evenings from 6-7pm

> What platforms will the group use to communicate and share documents?

- We will be using Google Doc for working on the document/sharing our ideas, and communicate through text in a group chat.

> Question of interest

- How does the population density of boroughs correlate with school quality scores in New York City?

> Description of the data:

- The data was collected by the city of New York, from Data.Gov
- One row from the quality of school file represents one school and its data for one particular year. For one row of the population density represents one borough. 
- This data set provides population projections by borough over time, including demographic breakdowns.
- The combined data set will allow us to examine relationships between population of borough and school quality indicators.

```{r}
 boroughs <- read.csv("/Users/hollybrikowski/Desktop/STAT240/data/Projected_Population_2010-2040_-_Summary.csv")
```

```{r}
schools <- read.csv("/Users/hollybrikowski/Desktop/STAT240/data/School_Quality_Reports_Data.csv")
```

```{r}
new_school <- schools %>%
 drop_na() %>%
  filter(School.Year >= "2020")
```

https://catalog.data.gov/dataset/school-quality-reports-data

https://catalog.data.gov/dataset/projected-population-2010-2040-summary

> Graph

- A scatter plot showing the correlation between borough population and average school quality scores. 
- Axes: Population Density (X), School Quality Score (Y).

> Methods 

- Linear regression to explore correlations and hypothesis testing to determine statistical significance.
- Null Hypothesis: there is not a relationship between the two
- Alternative Hypothesis: there is a relationship between the two